6.867 Problem Set 1

### 2015-12-10 Project/Latex/Paper.tex
[project] more writing.

We wanted to determine how our Naive Bayes implementation did compared to an off-the-shelf implementation of the same algorithm. In order to do so, we trained NLTK's multinomial Naive Bayes classifier on the same training data, and then evaluated the sentiment of 1,000 articles. A comparison of the two implementations is found below:

>>>>

We wanted to determine how our Naive Bayes implementation did compared to an off-the-shelf implementation of the same algorithm. In order to do so, we trained NLTK's multinomial Naive Bayes classifier on the same training data, and then evaluated the sentiment of 1,000 articles. A comparison of the two implementations is found below, where the columns indicate the prediction by the NLTK Naive Bayes implementation and the rows indicate the prediction by our implementation:

\vspace{10 mm}

\begin{tabular}{l | r r r}
\toprule
  & negative & neutral & positive\\
\midrule
negative & 0 & 54 & 0\\
neutral & 2 & 894 & 0\\
positive & 0 & 50 & 0\\
\end{tabular}

\vspace{10 mm}

Overall, we find 89.4\% agreement between the two algorithms. However, alarmingly, the NLTK implementation seems to predict neutral an overwhelming percentage of the time (99.8\% of the time). This warrants further investigation, and may be due to small differences in implementation, or peculiarities in the sample of 1,000 articles we chose to compare the two algorithms across. In any case, our algorithm seems to be performing in the same neighborhood as the NLTK implementation (if not better), so we feel relatively comfortable moving forward using our sentiment labels.
